POMDP comparisons across sigma_m, sigma_g

### 2017-12-28 appendix/appendix.Rmd
discount at 0.95

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99
```

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 60000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

>>>>

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.95
```

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 15000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

### 2017-12-28 appendix/appendixB.Rmd
discount at 0.95

```{r}
## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- .99
```

>>>>

```{r}
## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- .95
```
